Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-10-21 paper/paper.tex
edits
alteração com dados do zenodo
new zenodo repo

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of test transplantation and differential testing in
revealing functional bugs in popular \javascript\ engines.  Additional
contributions include: 1)~A number of bugs found and fixed.  We
reported a total of \totalBugsReported bugs.  Of these,
\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
fixed.  2)~An infrastructure for performing test transplantation and
differential testing. The source code produced and the generated data sets of tests
and bugs are publicly available online at the following link:

\dataRepo.

>>>>

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of test transplantation and differential testing in
revealing functional bugs in popular \javascript\ engines.  Additional
contributions include: 1)~A number of bugs found and fixed.  We
reported a total of \totalBugsReported bugs.  Of these,
\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
fixed.  2)~An infrastructure for performing test transplantation and
differential testing. The source code produced and the generated data sets of tests
and bugs are available on Zenodo~\footnote{https://zenodo.org/record/4116092} and online at the following link: \dataRepo.
